---
title: "Data Visualization"
author: "Quoc Anthony Doan"
format: 
  html:
    toc: true
    toc-depth: 5
editor: visual
---

## Setup

### Set the Seed for reproducibility

```{r}
set.seed(123)
```

### library

```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(arrow)
```

## Data

### Import

#### Paths

```{r}
mainDir <- 'data/cleaned_data'

subDir <- 'training_set_labels'
training_set_labels_path <- file.path(mainDir, subDir)


subDir <- 'training_set_features'
training_set_features_path <- file.path(mainDir, subDir)

subDir <- 'training_set'
training_set_path <- file.path(mainDir, subDir) 

subDir <- 'submission_format'
submission_format_path <- file.path(mainDir, subDir) 

subDir <- 'test_set_features'
test_set_features_path <- file.path(mainDir, subDir) 
```

#### Datasets

```{r}
training_set_labels_pq <- 
  read_parquet(
    paste(training_set_labels_path,"part-0.parquet", sep = "/"))
training_set_features_pq <- 
  read_parquet(
    paste(training_set_features_path,"part-0.parquet", sep = "/"))
training_set_pq <- 
  read_parquet(
    paste(training_set_path,"part-0.parquet", sep = "/"))
submission_format_pq <- 
  read_parquet(
    paste(submission_format_path,"part-0.parquet", sep = "/"))
test_set_features_pq <- 
  read_parquet(
    paste(test_set_features_path,"part-0.parquet", sep = "/"))
```

## Visualizing Distributions (univariate visualization)

Let's get a sense of the distribution of the data.

### Variables / Features

### `h1n1_concern`

```{r}
ggplot(training_set_pq, aes(x = h1n1_concern)) +
  geom_bar(aes(fill = h1n1_concern)) +
  labs(
    title = "Level of concern about the H1N1 flu",
    subtitle = "Visualization the distribution of h1n1_concern feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `h1n1_knowledge`

```{r}
ggplot(training_set_pq, aes(x = h1n1_knowledge)) +
  geom_bar(aes(fill = h1n1_knowledge)) +
  labs(
    title = "Level of knowledge about H1N1 flu",
    subtitle = "Visualization the distribution of h1n1_knowledge feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `behavioral_antiviral_meds`

```{r}
ggplot(training_set_pq, aes(x = behavioral_antiviral_meds)) +
  geom_bar(aes(fill = behavioral_antiviral_meds)) +
  labs(
    title = "Has taken antiviral medications (binary)",
    subtitle = "Visualization the distribution of behavioral_antiviral_meds feature",
    x = "False / True"
  ) +
  scale_color_colorblind()
```

### `behavioral_avoidance`

```{r}
ggplot(training_set_pq, aes(x = behavioral_avoidance)) +
  geom_bar(aes(fill = behavioral_avoidance)) +
  labs(
   title = "Has avoided close contact with others with flu-like symptoms. (binary)",
   subtitle = "Visualization the distribution of behavioral_avoidance feature",
   x = "False / True"
  ) +
  scale_color_colorblind()
```

### `behavioral_face_mask`

```{r}
ggplot(training_set_pq, aes(x = behavioral_face_mask)) +
  geom_bar(aes(fill = behavioral_face_mask)) +
  labs(
   title = "Has bought a face mask. (binary)",
   subtitle = "Visualization the distribution of behavioral_face_mask feature",
   x = "False / True"
  ) +
  scale_color_colorblind()
```

### `behavioral_wash_hands`

```{r}
ggplot(training_set_pq, aes(x = behavioral_wash_hands)) +
  geom_bar(aes(fill = behavioral_wash_hands)) +
  labs(
   title = "Has frequently washed hands or used hand sanitizer. (binary)",
   subtitle = "Visualization the distribution of behavioral_wash_hands feature",
   x = "False / True"
  ) +
  scale_color_colorblind()
```

### `behavioral_large_gatherings`

```{r}
ggplot(training_set_pq, aes(x = behavioral_large_gatherings)) +
  geom_bar(aes(fill = behavioral_large_gatherings)) +
  labs(
   title = "Has reduced time at large gatherings. (binary)",
   subtitle = "Visualization the distribution of behavioral_large_gatherings feature",
   x = "False / True"
  ) +
  scale_color_colorblind()
```

### `behavioral_outside_home`

```{r}
ggplot(training_set_pq, aes(x = behavioral_outside_home)) +
  geom_bar(aes(fill = behavioral_outside_home)) +
  labs(
   title = "Has reduced contact with people outside of own household. (binary)",
   subtitle = "Visualization the distribution of behavioral_outside_home feature",
   x = "False / True"
  ) +
  scale_color_colorblind()
```

### `behavioral_touch_face`

```{r}
ggplot(training_set_pq, aes(x = behavioral_touch_face)) +
  geom_bar(aes(fill = behavioral_touch_face)) +
  labs(
   title = "Has avoided touching eyes, nose, or mouth. (binary)",
   subtitle = "Visualization the distribution of behavioral_touch_face feature",
   x = "False / True"
  ) +
  scale_color_colorblind()
```

### `doctor_recc_h1n1`

```{r}
ggplot(training_set_pq, aes(x = doctor_recc_h1n1)) +
  geom_bar(aes(fill = doctor_recc_h1n1)) +
  labs(
   title = "H1N1 flu vaccine was recommended by doctor. (binary)",
   subtitle = "Visualization the distribution of doctor_recc_h1n1 feature",
   x = "False / True"
  ) +
  scale_color_colorblind()
```

### `doctor_recc_seasonal`

```{r}
ggplot(training_set_pq, aes(x = doctor_recc_seasonal)) +
  geom_bar(aes(fill = doctor_recc_seasonal)) +
  labs(
   title = "Seasonal flu vaccine was recommended by doctor. (binary)",
   subtitle = "Visualization the distribution of doctor_recc_seasonal feature",
   x = "False / True"
  ) +
  scale_color_colorblind()
```

### `chronic_med_condition`

```{r}
ggplot(training_set_pq, aes(x = chronic_med_condition)) +
  geom_bar(aes(fill = chronic_med_condition)) +
  labs(
   title = "Visualization the distribution of chronic_med_condition feature",
   subtitle = "Has any of the following chronic medical conditions: \nasthma or an other lung condition, diabetes, a heart condition, a kidney condition, \nsickle cell anemia or other anemia, a neurological or neuromuscular condition, \na liver condition, or a weakened immune system caused by a chronic illness \nor by medicines taken for a chronic illness. (binary)",
   x = "False / True"
  ) +
  theme(axis.text.x = element_text(vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `child_under_6_months`

```{r}
ggplot(training_set_pq, aes(x = child_under_6_months)) +
  geom_bar(aes(fill = child_under_6_months)) +
  labs(
   title = "Has regular close contact with a child under the age of six months. (binary)",
   subtitle = "Visualization the distribution of child_under_6_months feature",
   x = "False / True"
  ) +
  scale_color_colorblind()
```

### `health_worker`

```{r}
ggplot(training_set_pq, aes(x = health_worker)) +
  geom_bar(aes(fill = health_worker)) +
  labs(
   title = "Is a healthcare worker. (binary)",
   subtitle = "Visualization the distribution of health_worker feature",
   x = "False / True"
  ) +
  scale_color_colorblind()
```

### `health_insurance`

```{r}
ggplot(training_set_pq, aes(x = health_insurance)) +
  geom_bar(aes(fill = health_insurance)) +
  labs(
   title = "Has health insurance. (binary)",
   subtitle = "Visualization the distribution of health_insurance feature",
   x = "False / True"
  ) +
  scale_color_colorblind()
```

### `opinion_h1n1_risk`

```{r}
ggplot(training_set_pq, aes(x = opinion_h1n1_risk)) +
  geom_bar(aes(fill = opinion_h1n1_risk)) +
  labs(
    title = "Respondent's opinion about risk of getting sick with H1N1 flu without vaccine.",
    subtitle = "Visualization the distribution of opinion_h1n1_risk feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `opinion_h1n1_sick_from_vacc`

```{r}
ggplot(training_set_pq, aes(x = opinion_h1n1_sick_from_vacc)) +
  geom_bar(aes(fill = opinion_h1n1_sick_from_vacc)) +
  labs(
    title = "Respondent's worry of getting sick from taking H1N1 vaccine.",
    subtitle = "Visualization the distribution of opinion_h1n1_sick_from_vacc feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `opinion_seas_vacc_effective`

```{r}
ggplot(training_set_pq, aes(x = opinion_seas_vacc_effective)) +
  geom_bar(aes(fill = opinion_seas_vacc_effective)) +
  labs(
    title = "Respondent's opinion about seasonal flu vaccine effectiveness.",
    subtitle = "Visualization the distribution of opinion_seas_vacc_effective feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `opinion_seas_risk`

```{r}
ggplot(training_set_pq, aes(x = opinion_seas_risk)) +
  geom_bar(aes(fill = opinion_seas_risk)) +
  labs(
    title = "Respondent's opinion about risk of getting sick with seasonal flu without vaccine.",
    subtitle = "Visualization the distribution of opinion_seas_risk feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `opinion_seas_sick_from_vacc`

```{r}
ggplot(training_set_pq, aes(x = opinion_seas_sick_from_vacc)) +
  geom_bar(aes(fill = opinion_seas_sick_from_vacc)) +
  labs(
    title = "Respondent's worry of getting sick from taking seasonal flu vaccine.",
    subtitle = "Visualization the distribution of opinion_seas_sick_from_vacc feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `age_group`

```{r}
ggplot(training_set_pq, aes(x = age_group)) +
  geom_bar(aes(fill = age_group)) +
  labs(
    title = "Age group of respondent.",
    subtitle = "Visualization the distribution of age_group feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `education`

```{r}
ggplot(training_set_pq, aes(x = education)) +
  geom_bar(aes(fill = education)) +
  labs(
    title = "Self-reported education level.",
    subtitle = "Visualization the distribution of education feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `race`

```{r}
ggplot(training_set_pq, aes(x = race)) +
  geom_bar(aes(fill = race)) +
  labs(
    title = "Race of respondent.",
    subtitle = "Visualization the distribution of race feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

There is a huge skew for 'white'.

### `sex`

```{r}
ggplot(training_set_pq, aes(x = sex)) +
  geom_bar(aes(fill = sex)) +
  labs(
    title = "Sex of respondent.",
    subtitle = "Visualization the distribution of sex feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `income_poverty`

```{r}
ggplot(training_set_pq, aes(x = income_poverty)) +
  geom_bar(aes(fill = income_poverty)) +
  labs(
    title = "Household annual income of respondent with respect to 2008 Census poverty thresholds.",
    subtitle = "Visualization the distribution of income_poverty feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `marital_status`

```{r}
ggplot(training_set_pq, aes(x = marital_status)) +
  geom_bar(aes(fill = marital_status)) +
  labs(
    title = "Marital status of respondent.",
    subtitle = "Visualization the distribution of marital_status feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `rent_or_own`

```{r}
ggplot(training_set_pq, aes(x = rent_or_own)) +
  geom_bar(aes(fill = rent_or_own)) +
  labs(
    title = "Housing situation of respondent.",
    subtitle = "Visualization the distribution of rent_or_own feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `employment_status`

```{r}
ggplot(training_set_pq, aes(x = employment_status)) +
  geom_bar(aes(fill = employment_status)) +
  labs(
    title = "Employment status of respondent.",
    subtitle = "Visualization the distribution of employment_status feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `hhs_geo_region`

```{r}
ggplot(training_set_pq, aes(x = hhs_geo_region)) +
  geom_bar(aes(fill = hhs_geo_region)) +
  labs(
    title = "Visualization the distribution of hhs_geo_region feature",
    subtitle = "Respondent's residence using a 10-region geographic classification defined by \nthe U.S. Dept. of Health and Human Services. \nValues are represented as short random character strings.",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `census_msa`

```{r}
ggplot(training_set_pq, aes(x = census_msa)) +
  geom_bar(aes(fill = census_msa)) +
  labs(
    title = "Respondent's residence within metropolitan statistical areas (MSA) \nas defined by the U.S. Census.",
    subtitle = "Visualization the distribution of census_msa feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `household_adults`

```{r}
ggplot(training_set_pq, aes(x = household_adults)) +
  geom_bar(aes(fill = household_adults)) +
  labs(
    title = "Number of other adults in household, top-coded to 3.",
    subtitle = "Visualization the distribution of household_adults feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `household_children`

```{r}
ggplot(training_set_pq, aes(x = household_children)) +
  geom_bar(aes(fill = household_children)) +
  labs(
    title = "Number of other children in household, top-coded to 3.",
    subtitle = "Visualization the distribution of household_children feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

### `employment_industry`

```{r}
ggplot(training_set_pq, aes(x = employment_industry)) +
  geom_bar(aes(fill = employment_industry)) +
  labs(
    title = "Type of industry respondent is employed in. Values are represented as short random character strings.",
    subtitle = "Visualization the distribution of employment_industry feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```

```{r}
training_set_features_pq |> 
  count(employment_industry)

13330/nrow(training_set_features_pq)
```

About 50% of the respondents did not report and/or are missing `employment_industry`. Not sure how good this variable/feature is for predictive model.

### `employment_occupation`

```{r}
ggplot(training_set_pq, aes(x = employment_occupation)) +
  geom_bar(aes(fill = employment_occupation)) +
  labs(
    title = "Type of occupation of respondent. Values are represented as short random character strings.",
    subtitle = "Visualization the distribution of employment_occupation feature",
    x = "levels"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_color_colorblind()
```
```{r}
training_set_features_pq |> 
  count(employment_occupation)

13470/nrow(training_set_features_pq)
```

50% of the respondents did not report and/or are missing `employment_occupation`. Not sure how good this variable/feature is for predictive model.